### 2021-09-30 papers/thesis/resubmitted/ch1-introduction/introduction.tex
Added general framework to the intro (draft)

The structure of this thesis is as follows.

>>>>

% GENERAL FRAMEWORK
The construction of the spectral methods in this thesis follow a similar pattern that is worth detailing here as a general framework.
\begin{itemize}
	\item \textit{Define the domain of interest via a restriction of one coordinate in terms of the remainder, that uses a function $\rho$ that satisfies one of two conditions.}

		For example, for a domain in 2D space, we would define this as $\Omega := \bsset{(x,y) \in \R^2}{\alpha \le x \le \beta, \: \gamma \rho(x) \le y \le \delta \rho(x)}$.

	\item \textit{Express the multivariate and multi-parameter OPs as polynomials in cartesian coordinates.}

		The construction of the multivariate OPs takes its inspiration from the Koornwinder approach \cite{koornwinder1975two}. These OPs will be $d$-parameter, meaning that we can construct parameter lowering and raising operators for conversion between the OP bases.

	\item \textit{Derive expressions for multiplication of the OPs by the coordinates.}

	\item \textit{Use these relations to determine the entries to \enquote{Jacobi matrices} $J_x$, etc. that represent multiplication by the coordinates when applied to the degree-ordered vector of OPs $\bigP$.}

		These Jacobi matrices will be banded-block-banded in structure. In fact, due to the construction, they will be block-tridiagonal:
		\bseqn{
			J_{x/y} &= 
			\begin{pmatrix}
				B_{x/y,0} & A_{x/y,0} & & & & \\
				C_{x/y,1} & B_{x/y,1} & A_{x/y,1} & & & \\
				& C_{x/y,2} & B_{x/y,2} & A_{x/y,2}  & & & \\
				& & C_{x/y,3} & \ddots & \ddots & \\
				& & & \ddots & \ddots & \ddots \\
			\end{pmatrix}.
		}
		The degree-ordered vector of OPs, $\bigP$, can be thought of as being made up of ordered sub-vectors grouped by polynomial degree, $\bigP_n$ for $n \in \No$.

	\item \textit{Create a three-term recurrence for the vector of degree $n$ OPs by combining the systems $J_x \bigP = x \bigP$, etc.}

		The resulting three-term recurrence will have the form:
		\bseqn{
			\bigP_{n+1}(x,y) = -\Dnt (B_n-G_n(x,y)) \bigP_n(x,y) - \Dnt C_n  \, \bigP_{n-1}(x,y)
		}
		Here, the matrices $B_n$, $C_n$ and $G_n$ are defined via:
		\bseqn{
                    	C_n := 
                    		\begin{pmatrix}
                    			C_{x,n} \\
	                    		C_{y,n}
				\end{pmatrix} \: (n \ne 0), \quad
			B_n &:= 
				\begin{pmatrix}
                    			B_{x,n} \\
	                    		B_{y,n}
				\end{pmatrix}, \quad
			G_n(x,y) := 
                    		\begin{pmatrix}
					xI_{n+1} \\
	                    		yI_{n+1}
				\end{pmatrix}.
		}
		The matrices $\Dnt$ are left-inverses of the matrices $A_n$ respectively, which are defined similarly:
		\bseqn{		
			A_n &:=
				\begin{pmatrix}
                    			A_{x,n} \\
                    			A_{y,n}
				\end{pmatrix}, \quad
		}

	\item \textit{Use the multivariate version of the Clenshaw algorithm for evaluation of functions expanded in the OP basis.}

	\item \textit{Derive (sparse) relationships for various differential operations, and relations for incrementing and decrementing the parameter values of the OPs. Hence construct the sparse operator matrices representing these operations.}

		The differential operators may raise or lower parameter values, which is why the basis conversion operator matrices are required. Further operators may be constructed as combinations of others.

	\item \textit{Use the \enquote{operator Clenshaw algorithm} to construct operator matrices for the action of multiplying by a general function.}

		For instance, this would be useful for a variable coefficient in a Helmholtz example.
\end{itemize}

The structure of the remainder of thesis is as follows.
